---
title: "Conflict Analysis R Scripts 1"
subtitle: 'Data Loading and Standardization'
author: "Aimee Barciauskas, Harihara Subramanyam, Roger Cuscó"
date: "November 28, 2015"
output: pdf_document
---

## Data sub-selection by numbers:

* Created the table `city_day_event_counts_plus` (see database.md) which is table of number of conflict events per day per city in the U.S. between April 2013 and November 6, 2015.
* Started with 2,018 cities having conflicts since 2013, with a total of 1,507,041 events.
* Removed cities in Alaska and Hawaii
* Sub-select to 100 cities with the most data:
    * Summed the number of days per city represented, took the top 100
    * 82% of conflicts are represented by these top 100 cities
    * See `top_cities.sql`

```{r, echo=FALSE, warnings=FALSE, messages=FALSE}
library(RMySQL)
library(reshape)
library(ggplot2)
library(dplyr)
library(RColorBrewer)
setwd('~/Box Sync/abarciausksas/myfiles/conflicts_analysis_project/')
images_dir <- 'conflict_analysis_app/public/images/'
rcolors <- brewer.pal(11, 'Spectral')
source('scripts/r/helpers.R')
theme_set(theme_gray(base_size = 18))

con <- dbConnect(RMySQL::MySQL(), user="root", password="root", dbname = "gdelt")

res <- dbSendQuery(con, "select * from top_cities where sqldate > 20130701")
data <- dbFetch(res, n = -1)

# Standard data formatting
data$datef <- as.Date(as.character(data$sqldate), format = '%Y%m%d')
data$city <- paste0(data$name, ', ', data$admin1_code)
data$city <- factor(data$city)
data$population <- as.numeric(data$population)
```

# Data standardization

```{r, echo=FALSE, warnings=FALSE, messages=FALSE }
day_means <- tapply(data$num_conflicts, data$sqldate, FUN=mean)
day_means <- cbind(as.matrix(day_means), as.numeric(row.names(day_means)))
colnames(day_means) <- c('date_mean','sqldate')

day_sds <- tapply(data$num_conflicts, data$sqldate, FUN=sd)
day_sds <- cbind(as.matrix(day_sds), as.numeric(row.names(day_sds)))
colnames(day_sds) <- c('date_sd','sqldate')

data <- merge(data, day_means, by = 'sqldate', all.x = TRUE)
data <- merge(data, day_sds, by = 'sqldate', all.x = TRUE)

data$std_num_conflicts <- (data$num_conflicts - data$date_mean)/data$date_sd
```


```{r, echo=FALSE, warnings=FALSE, messages=FALSE}
#install.packages('Rmisc')
library(Rmisc)

plot1 <- ggplot(data = data, aes(x = datef, y = num_conflicts, color = city)) + geom_line() +
  theme(
    legend.position = "none",
    panel.background = element_blank())

plot2 <- ggplot(data = data, aes(x = datef, y = log(num_conflicts), color = city)) + geom_line() +
  theme(
    legend.position = "none",
    panel.background = element_blank())

plot3 <- ggplot(data = data, aes(x = datef, y = std_num_conflicts, color = city)) + geom_line() +
  theme(
    legend.position = "none",
    panel.background = element_blank())

png(paste0(images_dir,'summary_num_conflicts_raw.png'), bg = "transparent", width=1200, height=400, units='px')
multiplot(plot1, plot2, plot3, cols=3)
dev.off()
```

It's very noisy so we simplify the charts...

```{r, echo=FALSE, warnings=FALSE, messages=FALSE}
plot1 <- ggplot(data = data, aes(x = datef, y = num_conflicts, color = city)) + geom_smooth(method="loess", se=FALSE) + 
  scale_colour_manual(values=rep('#56B4E9',100)) +
  theme(legend.position = "none",
        panel.background = element_blank())

plot2 <- ggplot(data = data, aes(x = datef, y = log(num_conflicts), color = city)) + geom_smooth(method="loess", se=FALSE) + 
  scale_colour_manual(values=rep('#56B4E9',100)) +
  theme(legend.position = "none",
        panel.background = element_blank())

plot3 <- ggplot(data = data, aes(x = datef, y = std_num_conflicts, color = city)) + geom_smooth(method="loess", se=FALSE) + 
  scale_colour_manual(values=rep('#56B4E9',100)) +
  theme(legend.position = "none",
        panel.background = element_blank())

png(paste0(images_dir,'summary_num_conflicts_smooth.png'), bg = "transparent", width=1200, height=400, units='px')
multiplot(plot1, plot2, plot3, cols=3)
dev.off()
```
But added a log(num_conflicts) column given data looks mostly stationary.

```{r, echo=FALSE, warnings=FALSE, messages=FALSE}
data$log_num_conflicts <- log(data$num_conflicts)
```
