---
title: "Conflict Analysis R Scripts 3"
subtitle: 'Auto-Correlation'
author: "Aimee Barciauskas, Harihara Subramanyam, Roger Cuscó"
date: "November 28, 2015"
output: pdf_document
---

## Neighbors correlation

For analysis of networks, we use the standardized form of the number of conflicts. The first pass used the log number of conflicts, however this also demonstrated suspicious levels of fit.

```{r, echo=FALSE, warnings=FALSE, messages=FALSE }
library(lattice)
library(reshape2)
date_by_city_matrix <- data[,c('std_num_conflicts','datef','city')]

# fun aggregate needed as some cells are not represented -> 0
events_by_date_city <- dcast(data = date_by_city_matrix, formula = datef ~ city, value.var = 'std_num_conflicts', fun.aggregate = sum)

# Sanity check
# head(events_by_date_city[,'Tulsa, OK'], n = 20)
# head(data[data$city == 'Tulsa, OK',][,c('std_num_conflicts','datef')], n = 10)

# Make date column rownames
rownames(events_by_date_city) <- events_by_date_city$datef
events_by_date_city <- events_by_date_city[,setdiff(colnames(events_by_date_city), 'datef')]

X <- events_by_date_city

### HELPER FUNCTIONS
my.cov <- function(X) {
  n <- nrow(X)
  d <- data.frame(mean = colMeans(X))
  means <- t(do.call("cbind", replicate(n, d, simplify = FALSE)))
  diff_matrix <- as.matrix(X - means)
  1/(n-1) * t(diff_matrix) %*% diff_matrix
}
my.cor <- function(X) {
  cov.matrix <- my.cov(X)
  # expect a square matrix
  cor.matrix <- matrix(0, nrow = nrow(cov.matrix), ncol = nrow(cov.matrix))
  for (i in 1:ncol(cov.matrix)) {
    for (j in 1:nrow(cov.matrix)) {
      cor.matrix[i,j] <- cov.matrix[i,j]/(sqrt(cov.matrix[i,i])*sqrt(cov.matrix[j,j]))
    }
  }
  cor.matrix
}

X.cor <- my.cor(X)
X.m <- melt(X.cor)
```

## Neighborhoods

```{r, echo=FALSE, warnings=FALSE, messages=FALSE }
source('scripts/data_expoloration/lasso.R')
X <- events_by_date_city
# for every column of X, want to run lasso on all other columns
# update coeff matrix, should be pxp
lasso.coeffs <- matrix(0, ncol=ncol(X), nrow = ncol(X))
rownames(lasso.coeffs) <- colnames(X)
colnames(lasso.coeffs) <- colnames(X)
for (i in 1:ncol(X)) {
  city <- colnames(X)[i]
  y <- as.numeric(X[,city])
  Xmat <- as.matrix(X[,setdiff(1:ncol(X), i)])
  model <- lm(y ~ Xmat)
  # When using a z-score, this was up to 5000
  coeffs <- lasso.reg(y, Xmat, 100)
  lasso.coeffs[city,setdiff(1:ncol(lasso.coeffs),i)] <- as.numeric(coeffs)
}

lasso.coeffs.select <- lasso.coeffs
# Remove them if they don't like each other (e.g. negative or 0 correlation)
for (i in 1:ncol(lasso.coeffs)) {
  for (j in 1:ncol(lasso.coeffs)) {
    if ((lasso.coeffs[i,j] <= 0.02) || (lasso.coeffs[j,i] <= 0.02)) {
      lasso.coeffs.select[i,j] = 0
      lasso.coeffs.select[j,i] = 0
    }
  }
}
```

```{r, echo=FALSE, warnings=FALSE, messages=FALSE }
#install.packages("igraph")

## Load package
library(igraph)

g1 <- graph.adjacency(lasso.coeffs.select, weighted=T, mode = 'undirected')
g1 <- simplify(g1)
V(g1)$label <- colnames(events_by_date_city)
V(g1)$label.cex <- (degree(g1) - mean(degree(g1)))/20 + 1
V(g1)$degree <- degree(g1)
V(g1)$size <- (V(g1)$degree)

# interactive plot
#tkplot(g)
layout <- layout.sphere
autocurve.edges(g1)

## Compare with SPACE results
library(space)
# Choice of lambda was largely trial and error until a reasonable result.
results <- space.joint(as.matrix(events_by_date_city),lam1=10)
P.hat   <- results$ParCor
N <- ncol(X)
A.hat   <- 1*( P.hat != 0 ) - diag(rep(1,N))
dimnames(A.hat) <- list(colnames(X), colnames(X))
g2 <- graph.adjacency(A.hat, weighted=T, mode = 'undirected')
g2 <- simplify(g2)
V(g2)$label <- colnames(events_by_date_city)
V(g2)$label.cex <- (degree(g2) - mean(degree(g2)))/100 + 1
V(g2)$degree <- degree(g2)/2 + 1
V(g2)$size <- V(g2)$degree

# interactive plot
#tkplot(g)

png(paste0(images_dir,'analysis_network_lasso.png'), bg = "transparent", width=525, height=525, units='px')
plot(g1, layout=layout.sphere,
     vertex.label.family = "Helvetica",
     vertex.label.color = '#333333',
     vertex.color='lightskyblue1',
     vertex.frame.color='lightskyblue1',
     edge.color='lightskyblue1',
     margin=-0.15)
dev.off()

png(paste0(images_dir,'analysis_network_space.png'), bg = "transparent", width=525, height=525, units='px')
plot(g2, layout=layout.sphere,
     vertex.label.family = "Helvetica",
     vertex.label.color = '#333333',
     vertex.color='lightskyblue1',
     vertex.frame.color='lightskyblue1',
     edge.color='lightskyblue1',
     margin=-0.15)
dev.off()

png(paste0(images_dir,'analysis_network_lasso_hist.png'), bg = "transparent", width=450, height=300, units='px')
hist(V(g1)$degree, 30, main='Degree of vertices', xlab='Degree')
dev.off()

png(paste0(images_dir,'analysis_network_space_hist.png'), bg = "transparent", width=450, height=300, units='px')
hist(V(g2)$degree, 30, main='Degree of vertices', xlab='Degree')
dev.off()
```

## Analyze fit

```{r}
library(R.utils)

# Store results from each regression
A.hat.results <- cbind(A.hat, rsquared = rep(0, nrow(A.hat)))

for (i in 1:ncol(A.hat)) {
  city.name <- colnames(A.hat)[i]
  A.hat.city <- as.matrix(events_by_date_city) %*% diag(A.hat[,city.name])
  colnames(A.hat.city) <- cities
  
  A.hat.city.df <- as.data.frame(A.hat.city)
  
  A.hat.city.df <- A.hat.city.df[, colSums(isZero(A.hat.city.df)) != nrow(A.hat.city.df)]
  A.hat.city.df <- cbind(A.hat.city.df, city = events_by_date_city[,city.name])
  A.hat.city.df <- as.matrix(A.hat.city.df)
  
  model <- lm(city ~ ., as.data.frame(A.hat.city.df))
  RSS = sum(residuals(model)**2)
  TSS = sum((mean(A.hat.city.df[,'city']) - A.hat.city.df[,'city'])**2)
  rsquared = 1 - (RSS/TSS)
  A.hat.results[city.name,'rsquared'] = rsquared
}
```

Below, we create data for map visualization - e.g. city-city pairs with lat-long.

```{r}
cities <- data[,c('city','latitude','longitude')]
cities <- unique(cities)
rownames(cities) <- cities$city
map.data <- melt(A.hat)
map.data <- subset(map.data, !(value == 0))
map.data <- cbind(map.data,
                  rsquared = rep(0, nrow(map.data)),
                  latitude = rep(0, nrow(map.data)),
                  longitude = rep(0, nrow(map.data)))


# Add r-squared based on X1
# This is dumb but can't find a better way...
for (i in 1:nrow(map.data)) {
  city <- as.character(map.data[i,'X1'])
  map.data[i,'rsquared'] <- A.hat.results[city,'rsquared']
  map.data[i,'latitude'] <- cities[city,'latitude']
  map.data[i,'longitude'] <- cities[city,'longitude']
}

write.csv(map.data, file = 'networks.csv', row.names = FALSE)
```


### Evalute std_num_conflicts v. avg:same_region + avg:other_regions

```{r, echo=FALSE, warnings=FALSE, messages=FALSE }
# get the regions using k-means
cities <- data[,c('city','latitude','longitude')]
cities <- unique(cities)

X <- as.matrix(cities[,c('longitude','latitude')])

nclusters <- 5
# FIXME: K-means is not clustering as well horizontally
source('scripts/r/kmeansGdist.R')
res <- k.means(X, nclusters)
r.nks <- res$r.nks
colnames(r.nks) <- sapply('region.', paste0, 1:nclusters)
cities <- cbind(cities, r.nks)

regions <- factor(apply(cities, 1, function(x) which(x == 1)), 
                    labels = colnames(cities)[4:(nclusters+4-1)]) 
cities <- cbind(cities, regions)
regions.list <- sort(as.character(unique(regions)))

library(ggmap)

map <- NULL
mapUS <- borders("state")
map <- ggplot() + mapUS
map <- map + 
  geom_text(data = cities, 
             aes(x = longitude, y = latitude, label = city, colour = regions), size = 5, vjust = .5, hjust = .8) +
  theme(panel.background = element_blank())

png(paste0(images_dir,'analysis_kluster_map.png'), bg = "transparent", width=1000, height=600, units='px')
map
dev.off()

# Matrix of coefficients for region effects for each city
# ncities x nregions + 1 (same region)
region_coeffs <- matrix(nrow=nrow(cities), ncol=length(regions.list)+1)
dimnames(region_coeffs) <- list(unique(cities$city), c('same_region', regions.list))

region_day_avgs_mat <- matrix(nrow=nrow(events_by_date_city), ncol=length(regions.list)+3)
dimnames(region_day_avgs_mat) <- list(1:nrow(events_by_date_city), c('datef','city','same_region', regions.list))

# for every city, calculate avg same_region and avg_other_regions
# doing counts so using glm - poisson
for (i in 1:nrow(cities)) {
  city <- cities[i,]
  region <- city$regions
  same_region_cities <- setdiff(cities[cities$regions == region,]$city, city$city)
  day_avgs_same_region <- rowMeans(events_by_date_city[,same_region_cities])

  region_avgs <- list()
  region_avgs[['same_region']] = day_avgs_same_region
  # get averages for other regions
  for (ridx in 1:length(regions.list)) {
    c_region <- regions.list[ridx]
    if (!c_region == as.character(region)) {
      c_region_cities <- cities[cities$regions == c_region,]
      avg_c_region <- rowMeans(events_by_date_city[,as.character(c_region_cities$city)])
      region_avgs[[c_region]] <- avg_c_region
    } else {
      region_avgs[[c_region]] <- 0
    }
  }
  
  region_avgs_df <- as.matrix(as.data.frame(region_avgs))
  city_name <- toString(city$city)
  rad <- cbind(rep(city_name, nrow(region_avgs_df)), region_avgs_df)
  rad <- cbind(unique(as.character(data$datef)), rad)
  
  region_day_avgs_mat <- rbind(region_day_avgs_mat, rad) 

  model <- lm(events_by_date_city[,as.character(city$city)] ~ 0+region_avgs_df)
  coeffs <- coefficients(model)
  names(coeffs) <- lapply(names(coeffs), function(n) { gsub("region_avgs_df", "", n) })

  for (ridx in 1:length(regions.list)) {
    c_region <- regions.list[ridx]
    region_coeffs[as.character(city$city),c_region] = coeffs[c_region]
  }
  region_coeffs[as.character(city$city),'same_region'] = coeffs['same_region']
}


final <- region_day_avgs_mat[!(is.na(region_day_avgs_mat[,'same_region'])),]
final <- as.data.frame(final, stringsAsFactors=FALSE)
final$city <- factor(final$city)
final$datef <- as.Date(as.character(final$datef), format = '%Y-%m-%d')
for (i in c('same_region', regions.list)) {
  final[,i] <- as.numeric(final[,i])
}

png(paste0(images_dir,'analysis_kluster_region_coeffs_boxplot.png'), bg = "transparent", width=800, height=600, units='px')
boxplot(region_coeffs, use.cols = TRUE, ylim=c(-0.5,1.5), main = 'Quantiles of Region Effects Across 100 cities', ylab='Quantiles of coefficients', xlab ='Regions')
dev.off()
```