---
title: "SPACE"
author: "Aimee Barciauskas"
date: "November 28, 2015"
output: html_document
---

# SPACE Analysis of Networks

Data standardization

```{r}
library(RMySQL)
library(reshape)
library(ggplot2)
library(dplyr)

con <- dbConnect(RMySQL::MySQL(), user="root", password="root", dbname = "gdelt")

res <- dbSendQuery(con, "select * from top_cities where sqldate > 20130401")
data <- dbFetch(res, n = -1)

# Standard data formatting
data$datef <- as.Date(as.character(data$sqldate), format = '%Y%m%d')
data$city <- paste0(data$name, ', ', data$admin1_code)

## Removing Washington, D.C. (for now)
data <- subset(data, geonameid != '4140963')

day_means <- tapply(data$num_conflicts, data$sqldate, FUN=mean)
day_means <- cbind(as.matrix(day_means), as.numeric(row.names(day_means)))
colnames(day_means) <- c('date_mean','sqldate')

data <- merge(data, day_means, by = 'sqldate', all.x = TRUE)

data$std_num_conflicts <- (data$num_conflicts - data$date_mean)
```

Melt data into ncities x ncities

```{r}
library(reshape2)
date_by_city_matrix <- data[,c('num_conflicts','datef','city')]

# fun aggregate needed as some cells are not represented -> 0
events_by_date_city <- dcast(data = date_by_city_matrix, formula = datef ~ city, value.var = 'num_conflicts', fun.aggregate = sum)

# Sanity check
# head(events_by_date_city[,'Tulsa, OK'], n = 20)
# head(data[data$city == 'Tulsa, OK',][,c('std_num_conflicts','datef')], n = 10)

# Make date column rownames
rownames(events_by_date_city) <- events_by_date_city$datef
events_by_date_city <- events_by_date_city[,setdiff(colnames(events_by_date_city), 'datef')]

X <- events_by_date_city
```

### SPACE Algorithm

1) Estimate K -> the concentration matrix, K[i,j] is the concentration for the ith and jth pair
2) Given an estimate k.hat[i,i], minimize (the error for the ith group + penalty)
   The estimate is sum( (rhos[,!i]) * sqrt(k.hat[j,j]/k.hat[i,i]) y[,!i])
   The penalty is lambda * sum(rhos)
3) Given 2's estimate of rho[i,j] estimate k[i,i] as residual variance
4) Check for convergence
5) Estimate the nondiagonal entries of K as K[i,j] = -rho[i,j] * sqrt(K[i,i] * K[j,j])

```{r}
my.lm <- function(y, X) solve(t(X)%*%X) %*% t(X) %*% y

library(MASS)
K <- solve(cov(X))

i <- 1
yit <- X[,i]
yjt <- as.matrix(X[,setdiff(1:ncol(X), i)])

model <- my.lm(yit, yjt)
(initial.betas <- model)

for (j in 2:n)
j <- 2
k.jj <- K[j,j]
k.ii <- K[i,i]
beta.j <- initial.betas[j-1]
rho.j <- sqrt(k.ii*k.jj)/beta.j
```

